Incentivizing Exploration with Unbiased History

### 2018-11-02 2level.tex
Small edit.
some comments

\begin{theorem}\label{thm:2level}
The \2LEVEL with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
\[ \reg(T) \leq O_K\left( T^{2/3}\, \log(T)^{1/3} \right).\]
\end{theorem}

@@

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent forms its estimates according to the same \emph{estimate function}: a function $f$ from subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f(m_t)$.
\end{assumption}

>>>>

\begin{theorem}\label{thm:2level}
The \2LEVEL with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
\[ \reg(T) \leq O_K\left( T^{2/3}\, (\log T)^{1/3} \right).\]
\end{theorem}

@@

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to the same \emph{estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
\end{assumption}

### 2018-11-02 model.tex

We allow a much more permissive model, characterized by the following assumption:%
\footnote{In what follows, we make this assumption without further notice.}

\jmcomment{Should we emphasize heterogeneity here?}
%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

>>>>

We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average. Formally, the model is characterized by the following assumption (which we make without further notice).

%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
